HydroFlow: A New Dataflow Programming Language

### 2022-10-31 paper.tex
Because it matters to Joe, let's throw some almost-real-looking text into a PLDI-formatted document!
wip

>>>>

\section{An overview of the HydroFlow language}
\label{sec:hydroflow-overview}

Our basic goals for this section are to say:

\begin{itemize}
\item Hydroflow is a streaming programming language that transfers lattice elements
\item HydroFlow assembles operators (as Rust functions) into a dataflow graph using a surface syntax
\item HydroFlow makes independently-scheduled units, which we call _compiled components_, explicit; the surface syntax figures this out for you though.
\item Some amount of properties?  
\end{itemize}

We now review the syntax and basic user-facing features of HydroFlow, including its programming model, extensible operators, and the user-facing portions of its type system.

HydroFlow is a stream-oriented programming language, deeply embedded within Rust.  A HydroFlow program consists of a sequence of _operator_ definitions, followed by a description of a _dataflow graph_ which assemble instances of these operators into a dataflow computation.
